\chapter{September}

\section{Fourth week - 2.sept}
This week we were handed another task from Anders Hafreager (we have sort of become his staff now, it seems). The task was to translate a existing program written in Fortran to C++, and write the code in a parallal manner. The program is called distance\_to\_atom.cpp. \\
The idea behind the code:\\
We divide the system into a given number of voxels, and represent the voxels by a three-dimensional matrix, $\mat{M}$ which will store the distances from the center of the voxels to the nearest atoms. Each process iterates all the atoms, and each atom ``let'' the neighboring voxels know it exists, and if the distance from the atom to voxel is smaller than the distance the voxel already had stored, the new distance is stored in the matrix $\mat{M}$. By neighboring voxels I mean all the voxels within a distance, max\_distance, from the atom. This distance is given by the user. This means that voxels far away from any atoms may not register any atoms. In those cases the corresponding elements in $\mat{M}$ is just what the matrix was initialized with.
We initialize the matrix, $\mat{M}$, with a distance equal to half the system size, $L_2$. Since we assume periodic boundaries we know that half the system size is the largest distance we will find (maybe an idea to initialize with max\_distance instead?)\\
As of wednesday, each process have to load all the atoms. This is a lot of data, and completely unnecessary.\\

On monday I had a meeting with my supervisor, where I asked him to help me set some deadlines. The next thing he wanted me to do, was to passivate my system. This should be done within 2-3 weeks.\\
On thursday we (Hafreager, Trømborg, Filip, Kjetil, Mathilde) had our first code review. We went through distance\_to\_atom.cpp, and after some name changes and a few bug fixes, the program was approved and included in the master branch of base\_code. My movie\_function branch was also merged with the master branch (mdconfig).
\begin{framed}
\underline{This weeks product}:\\
Filip and I created the parallel program distance\_to\_atom.cpp. The master log was created. Had our first code review.
\end{framed}
\section{Fifth week - 9.sept}
\section{Sixth week - 16.sept}